\LARGE \bf Grasp Metric for Gaussian Proccess Implicit Surface Representation of Shape Uncertainity

### 2014-07-04 paper.tex
Not dead anymore!  Added expected center of mass calculation.  Some more refactoring and typo fixing.  Done for the night, didnt read past distribution on center of mass so far.

 For the following derivations we use the following notation.
 $\theta(x) = \lbrace \mu(x),\Sigma(x) \rbrace$, hence $\theta(x)$ is a tuple consisting of the mean and covariance functions given by the trained GPIS.
We further assume that the contacts on the gripper approach along a line of action: $x = \gamma(t): R \rightarrow R^d$.
% TODO: Michael, I changed this from voxel grid because we're modeling a continuous space not a voxel grid, the voxel grid willbe an artifact of our integration/sampling strategies.
We assume a bounded rectangular workspace.
The line segment has endpoints $a,b$ that are defined as the start of the gripper and the intersection of the line with the end of the workspace respectively, as shown in Fig.
 \ref{fig:line_of_action}.
 % TODO: Draw a box around the workspace to show that b intersects the end of the workspace and draw a gripper approaching from a.  Also make A and B lowercase in the figure.
 We also define the function $f(x): \mathbb{R}^d \rightarrow \mathbb{R}$ as $f(x) = \mu(x)$ and an implicit surface $\mathcal{S} = \{ x \ | \ f(x) = 0 \}$.
% TODO: Michael, did I fill this in correctly? It was left blank initially.

@@

\subsection{Distribution on Surface Normals} 
The distribution of surface normals $P(n_i = k)$ can be calculate as follows.
First we assume that some function exists $h(x) = \lbrace \mu_{\nabla}(x), \Sigma_{\nabla}(x) \rbrace$, hence given a point $x$ it returns the parameters for a Gaussian distribution around the gradient.
this function can be computed via learning the gradient \cite{gradient} or analytical differentiation of $f(x)$.
We note though that both methods yields a Gaussian distribution.
We now demonstrate how to marginalize out the contact distribution and compute $P(n_i = k)$\\

@@

Which over the voxel grid turns into:

@@

\subsection{Distribution on Center of Mass} Zoe fill out or we all die :-(

@@

\begin{theorem}
For any grasp g, we have $0 \leq Q_l^-(g) \leq Q(g)$.
Furthermore, $||Q(g) - Q^-_l(g)|| \rightarrow 0$ as $l \rightarrow \infty$ when $Q_l^-(g)$ is computed using a uniform approximation of the friction cones with $l$ edges. \\
\end{theorem}

>>>>

 For the following derivations we use the following notation.
 $\theta(x) = \lbrace \mu(x),\Sigma(x) \rbrace$, hence $\theta(x)$ is a tuple consisting of the mean and covariance functions given by the trained GPIS.
We further assume that the contacts on the gripper approach along a line of action: $x = \gamma(t): R \rightarrow R^d$.
% TODO: Michael, I changed this from voxel grid because we're modeling a continuous space not a voxel grid, the voxel grid willbe an artifact of our integration/sampling strategies.
We assume a bounded rectangular workspace $\mathcal{R}$.
The line segment has endpoints $a,b$ that are defined as the start of the gripper and the intersection of the line with the end of the workspace respectively, as shown in Fig.
 \ref{fig:line_of_action}.
 % TODO: Draw a box around the workspace to show that b intersects the end of the workspace and draw a gripper approaching from a.  Also make A and B lowercase in the figure.
 We also define the function $f(x): \mathbb{R}^d \rightarrow \mathbb{R}$ as $f(x) = \mu(x)$ and an implicit surface $\mathcal{S} = \{ x \ | \ f(x) = 0 \}$.
% TODO: Michael, did I fill this in correctly? It was left blank initially.

@@

\subsection{Distribution on Surface Normals} 
The distribution of surface normals $P(n_i = k)$ can be calculate as follows.
First we assume that some function exists $h(x) = \lbrace \mu_{\nabla}(x), \Sigma_{\nabla}(x) \rbrace$, hence given a point $x$ it returns the parameters for a Gaussian distribution around the gradient.
this function can be computed via learning the gradient \cite{gradient} or analytical differentiation of $f(x)$.
We note that both methods yield a Gaussian distribution.
We now demonstrate how to marginalize out the contact distribution and compute $P(n_i = k)$\\

@@

We then discretize the curve and approximate the integral by a sum:

@@

\subsection{Distribution on Center of Mass}

We define the quantity $\mathcal{D}(x) = \int_{-\infty}^{0} p(f(x) =  s \ | \ \theta(x)) ds$ and note that it is equal to the probability that x is interior to the surface under the current observations.
We assume that the object has uniform mass density and then $\mathcal{D}(x)$ is the expected mass density at x.
Then we can find the expected center of mass as:

\begin{equation}
  \mathcal{C} 
  =
  \frac
    {\int_{\mathcal{R}}x \mathcal{D}(x) dx}
    {\int_{\mathcal{R}}  \mathcal{D}(x) dx}
\end{equation}

which can be approximated by sampling $\mathcal{R}$ uniformly in a voxel grid and approximating the spatial integral by a sum.

@@

\begin{theorem}
  \cite{pokorny2013classical}
For any grasp g, we have $0 \leq Q_l^-(g) \leq Q(g)$.
Furthermore, $||Q(g) - Q^-_l(g)|| \rightarrow 0$ as $l \rightarrow \infty$ when $Q_l^-(g)$ is computed using a uniform approximation of the friction cones with $l$ edges. \\
\end{theorem}
